---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# Package FCO - Flexible Cutoffs for Model Fit Evaluation in Covariance-Based Structural Models

## Changes in FCO
### FCO 0.69
- Bug fixes in gen_fit for OS compatibility
- Improvements in the vignette

---
### FCO 0.67
- First stable release

## Description
The goal of FCO is to to derive flexible cutoffs for fit indices in Covariance-based Structural Equation Modeling based on the paper by Niemand & Mai (2018). Flexible cutoffs are an alternative to fixed cutoffs - rules-of-thumb - regarding an appropriate cutoff for fit indices such as CFI or SRMR. It has been demonstrated that these flexible cutoffs perform better than fixed cutoffs in grey areas where misspecification is not easy to detect. The package provides an alternative to the tool at flexiblecutoffs.org as it allows to tailor flexible cutoffs to a given dataset and model, which is so far not available in the tool. The package simulates fit indices based on a given dataset and model and then estimates the flexible cutoffs. Some useful functions, e.g., to determine the GoF or BoF-nature of a fit index, are provided. So far, additional options for a relative use (is a model better than another?) are provided in an explorative manner.

## Installation

You can install the development version of FCO from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ThomasNiemand/FCO")
```

## Example

This is the basic usage for FCO in case of deriving flexible cutoffs for a single model:

```{r example}
library(FCO)
library(lavaan)
#Data from bb1992
mod <- "
F1 =~ Q5 + Q7 + Q8
F2 =~ Q2 + Q4
F3 =~ Q10 + Q11 + Q12 + Q13 + Q18 + Q19 + Q20 + Q21 + Q22
F4 =~ Q1 + Q17
F5 =~ Q6 + Q14 + Q15 + Q16
"

#Empirical fit
res <- cfa(mod, data = bb1992)
fitmeasures(res, fit.measures = c("CFI", "SRMR"))

#Flexible cutoffs for this model
fits.single <- gen_fit(mod1 = mod, x = bb1992, rep = 100)
flex_co(fits = fits.single, index = c("CFI", "SRMR"))

#Use recommend function
recommend(fits.single)
```
